Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-10-22 paper/paper.qmd
Add files via upload

---
title: "Forecasting US Presidential Election Results Using Bayesian Prediction"
author: 
  - YiZhuo Li
  - Zhibin Huang

date: today
date-format: long
abstract: "This article aims to use Bayesian prediction methods to predict the results of the US presidential election. By summarizing public opinion survey data, we can understand the candidate's support rate."

@@

# Introduction
In today's era of information explosion, predicting the outcome of the US presidential election has become a complex and delicate task. With the constantly changing opinions of voters and the influence of numerous variables, traditional single opinion polls are no longer able to accurately capture the dynamics of elections. As Pasek (2015) pointed out, a single opinion poll may produce misleading results due to various sources of error such as sampling errors, question wording, interviewer characteristics, and lack of response. In order to improve the accuracy of predictions, this analysis adopted the views of Blumenthal (2014) and Pasek (2015), using Bayesian prediction methods and poll aggregation strategies to obtain a deeper and more comprehensive understanding of candidate support rates.
The study first introduced data preparation and variable description, with a focus on the percentage of support rates and indicators of opinion poll agencies. Then, we defined and fitted a Bayesian model to estimate the candidate's support rate, which can reduce the uncertainty of quantitative parameters through posterior distribution, enhance the credibility of analysis results, and allow the introduction of prior information to improve accuracy.
The flexibility of Bayesian models enables them to effectively integrate data from multiple polling companies, reduce noise, and provide more stable predictions. Through posterior estimation of model parameters, we found that the overall average support rate was about 14.35%, with a standard deviation of about 15.39%, indicating significant variability between different survey results. Our model prediction shows that Trump is most likely to win with an average approval rating of 35.52%, followed by Biden with 28.90%. Although Biden has withdrawn from the election, his approval rating remains high, which has raised concerns about the effectiveness of the model and data processing. So, we discussed the possible limitations of the model, including the quality of input data, prior assumptions of the model, and biases in the survey data itself. We believe that when analyzing public opinion polls, it is crucial to use the latest and accurate data as well as a reasonable model structure.

@@

We use the statistical programming language R [@citeR], with the goal of studying poll of poll data to obtain more information about presidential elections. The Poll of Polls is a comprehensive dataset that combines public surveys from multiple pollsters, including key data such as methodology, states, and answers used by each pollster. Through simple data cleaning and processing, we obtained percentage data, which is the support rate of each candidate in different pollsters. By modeling this variable, I believe we can obtain more meaningful information.

@@

## Modelling
The Bayesian model can be expressed with the following equations:

@@

pollster_results <- data.frame(
  pollster_id = 1:length(pollster_means),
  mean_effect = pollster_means
)
```
# Figure results

@@

ggplot(top_candidates, aes(x = "", y = mean_percentage, fill = answer)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") +
  labs(title = "  Vote Percentage Distribution of Top Candidates") +
  theme_void() +
  theme(legend.title = element_blank(),
        plot.title = element_text(hjust = 0.6, size = 16, face = "bold")) + 
  scale_fill_brewer(palette = "Set3") + 
  geom_text(aes(label = sprintf("%.2f%%", mean_percentage)), 
            position = position_stack(vjust = 0.5), 
            color = "black", 
            size = 5,  
            check_overlap = TRUE) 
```
\newpage

@@

# Appendix
## Appendix A
Online panel is a method of using Internet technology to conduct research. It collects data by recruiting a group of volunteers who are willing to participate in multiple online surveys. These volunteers, i.e. panel members, typically receive survey questionnaires via email or other online channels and are expected to complete these questionnaires. The advantage of this method is that it can quickly and cost effectively obtain information from a large number of participants. However, due to the voluntary participation of panel members, this may lead to sample selection bias, meaning that these members may not fully represent the diversity of the entire population. For example, some groups may be more inclined to join the panel because they are more familiar with or interested in technology, while other groups may be unable to participate due to lack of Internet access or other obstacles. In the study of political attitudes and behaviors, this bias is particularly noteworthy as it may affect the accuracy of election predictions and policy analysis.
Despite these potential biases, online panels still have the potential to collect representative data. If it can be ensured that the samples are obtained through probability sampling, that is, randomly selecting samples to ensure that each member has the same chance of being selected, then online panels can become a valuable tool in social science research. The transparency and replicability of this method make it particularly important when comparing the accuracy and representativeness of different survey methods. By combining advanced technology and social science research, online panels can help researchers better understand the complexity of election dynamics, attitude formation, and social and political behavior.

## Appendix B

>>>>

---
title: "Forecasting US Presidential Election Results Using Bayesian Prediction"
author: 
  - YiZhuo Li
  - Zhibin Huang
date: today
date-format: long
abstract: "This article aims to use Bayesian prediction methods to predict the results of the US presidential election. By summarizing public opinion survey data, we can understand the candidate's support rate."

@@

# Introduction
In today's era of information explosion, predicting the outcome of the US presidential election has become a complex and delicate task. With the constantly changing opinions of voters and the influence of numerous variables, traditional single opinion polls are no longer able to accurately capture the dynamics of elections. As Pasek [@Pasek2015] pointed out, a single opinion poll may produce misleading results due to various sources of error such as sampling errors, question wording, interviewer characteristics, and lack of response. In order to improve the accuracy of predictions, this analysis adopted the views of Blumenthal [@Blumenthal2014] and Pasek [@Pasek2015], using Bayesian prediction methods and poll aggregation strategies to obtain a deeper and more comprehensive understanding of candidate support rates.

The study first introduced data preparation and variable description, with a focus on the percentage of support rates and indicators of opinion poll agencies. Then, we defined and fitted a Bayesian model to estimate the candidate's support rate, which can reduce the uncertainty of quantitative parameters through posterior distribution, enhance the credibility of analysis results, and allow the introduction of prior information to improve accuracy.

The flexibility of Bayesian models enables them to effectively integrate data from multiple polling companies, reduce noise, and provide more stable predictions. Through posterior estimation of model parameters, we found that the overall average support rate was about 14.35%, with a standard deviation of about 15.39%, indicating significant variability between different survey results. Our model prediction shows that Trump is most likely to win with an average approval rating of 35.52%, followed by Biden with 28.90%. Although Biden has withdrawn from the election, his approval rating remains high, which has raised concerns about the effectiveness of the model and data processing. So, we discussed the possible limitations of the model, including the quality of input data, prior assumptions of the model, and biases in the survey data itself. We believe that when analyzing public opinion polls, it is crucial to use the latest and accurate data as well as a reasonable model structure.

@@

We use the statistical programming language R [@citeR], with the goal of studying poll of poll data to obtain more information about presidential elections [@FiveThirtyEight_Polls]. The Poll of Polls is a comprehensive dataset that combines public surveys from multiple pollsters, including key data such as methodology, states, and answers used by each pollster. Following @tellingstories, we start with simple data cleaning and processing, we obtained percentage data, which is the support rate of each candidate in different pollsters. By modeling this variable, I believe we can obtain more meaningful information.

@@

## Model set-up
The Bayesian model can be expressed with the following equations:

@@

pollster_results <- data.frame(
  pollster_id = 1:length(pollster_means),
  mean_effect = pollster_means
)
```
# Results

@@

ggplot(top_candidates, aes(x = "", y = mean_percentage, fill = answer)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") +
  labs(title = "  Vote Percentage Distribution of Top Candidates") +
  theme_void() +
  theme(legend.title = element_blank(),
        plot.title = element_text(hjust = 0.4, size = 16, face = "bold")) + 
  scale_fill_brewer(palette = "Set3") + 
  geom_text(aes(label = sprintf("%.2f%%", mean_percentage)), 
            position = position_stack(vjust = 0.5), 
            color = "black", 
            size = 5,  
            check_overlap = TRUE) 
```

@@

# Appendix
## Appendix A
Online panel is a method of using Internet technology to conduct research. It collects data by recruiting a group of volunteers who are willing to participate in multiple online surveys. These volunteers, i.e. panel members, typically receive survey questionnaires via email or other online channels and are expected to complete these questionnaires. The advantage of this method is that it can quickly and cost effectively obtain information from a large number of participants. However, due to the voluntary participation of panel members, this may lead to sample selection bias, meaning that these members may not fully represent the diversity of the entire population. For example, some groups may be more inclined to join the panel because they are more familiar with or interested in technology, while other groups may be unable to participate due to lack of Internet access or other obstacles. In the study of political attitudes and behaviors, this bias is particularly noteworthy as it may affect the accuracy of election predictions and policy analysis.

Despite these potential biases, online panels still have the potential to collect representative data. If it can be ensured that the samples are obtained through probability sampling, that is, randomly selecting samples to ensure that each member has the same chance of being selected, then online panels can become a valuable tool in social science research. The transparency and replicability of this method make it particularly important when comparing the accuracy and representativeness of different survey methods. By combining advanced technology and social science research, online panels can help researchers better understand the complexity of election dynamics, attitude formation, and social and political behavior.
